Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-17 paper/structureScene.tex
Edit discussion on late integration results

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to separately characterize distinct acoustic events beyond the scale of about one second. \ja{This is not suggested since the scattering transform is computed at $T=372\,\mathrm{ms}$ and so cannot be expected to capture larger-scale structures. Rather, this says something about the non-stationarity of the audio signals and the fact that we cannot characterize them by some set of summary statistics.}
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.

>>>>

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This suggests that there is relevant variability in scales beyond the window size $T = 372~\mathrm{ms}$ that is not captured by averaging the scattering transform in time (early integration). One potential solution to this is to increase the scale of the second-order modulation wavelets from $J_2 = 12$ octaves to some larger value. This does not result in any performance gain, however (results not shown). What does help is the late integration, since it allows the SVM to successfully classify the few short extracts that characterize the scene which are then used to classify the whole scene through the majority vote. Since the scattering transform, even with larger values of $J_2$, is not able to separate out these short, discriminative sound events, delegating this task to the late-integrated results in a more powerful classification system.
